\LARGE \bf How Children Perceive and Interact with a Robot that Behaves Unexpectedly - The Domino Experiment

### 2014-09-04 domino-study_hri15.tex
Added all missing figures in Julia's original paper

%\begin{figure}[!h]
%  \centering
%\subfloat[total number (count, \%)]    
%    {\label{fig:domino-action-count}\includegraphics[height=5cm]{domino_actions-pie.pdf}}
%%  \hspace{0.3cm}
%\subfloat[annotation duration, (\%)]    
%    {\label{fig:domino-action-time}\includegraphics[height=5cm]{domino_duration-pie.pdf}}
%
%  \caption[Total Number and Duration of Children's Actions with Ranger]{\small \textbf{Children's actions with Ranger.} (a) shows the total number of the counted actions that were annotated in the videos, (b) shows the total annotation duration percentage of these actions (the total duration of all coded actions are considered as 100\%, not the duration of the scenario).}
%  \label{fig:domino-actions-pie}
%\end{figure}

@@

%\begin{figure}[!b] 
%\centering 
%\includegraphics[width=0.99\columnwidth]{domino-time-all.pdf} 
%\caption[Number and Type of Actions for Each Run]{\small \textbf{Number and type of actions for each run} (average for one child per minute). Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9). The first 7 runs correspond to the \textit{expected phase}, the second 7 runs correspond to the \textit{unexpected phase}. Especially during run 2.3, the first time when the robot showed an unexpected behavior, children tended to \textit{look} more at the experimenter. During the unexpected phase, also \textit{talk} and \textit{gesture} seem to be increased. The specific values comparing the expected and unexpected phases overall are presented in Table \ref{tab:domino-conditions}, page~\pageref{tab:domino-conditions}.}
%\label{fig:domino-time-all} 
%\end{figure}

@@

%\begin{figure}[!h] 
%\centering 
%\includegraphics[width=0.9\columnwidth]{domino-actions-perrun.pdf} 
%\caption[Total Number of Actions for Each Run per Condition]{\small \textbf{Total number of actions for each run per condition} (average for one child per minute). Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9). Especially during run 2.3, the first time when the robot showed an unexpected behavior, children interact more with the robot, as well as during run 2.7 when the robot misbehaved again after two correct runs. Another increase of actions is during the very last run.}
%\label{fig:domino-time-condition-one} 
%\end{figure}		
%

@@

%\begin{figure}[!t] 
%\centering 
%\includegraphics[width=0.5\columnwidth]{domino-engagement-condition.pdf} 
%\caption[Engagement Actions in Expected and Unexpected Phase]{\small \textbf{Average number of engagement actions in expected and unexpected phase.} In all three behavior conditions, children engage more in the unexpected phase. In general, the \textit{lost} and \textit{mistake} misbehavior are more engaging than the \textit{disobeying} behavior.} 
%\label{fig:domino-engagement-condition} 
%\end{figure}

@@

%\begin{figure}[!h] 
%\centering 
%\includegraphics[width=0.99\columnwidth]{domino-time-active.pdf} 
%\caption[Engagement Actions for Each Run]{\small \textbf{Engagement actions for each run} (without explore). Average for one child per minute.}
%\label{fig:domino-time-active} 
%\end{figure}

@@

%\begin{figure}[!h]
%  \centering
%\subfloat[disobey3, boy S15]    
%    {\label{fig:domino-diff-group1}\includegraphics[height=4cm]{domino-disobey3_S15.pdf}}
%%  \hspace{0.3cm}
%\subfloat[disobey3, boy S16]    
%    {\label{fig:domino-diff-group2}\includegraphics[height=4cm]{domino-disobey3_S16.pdf}}\\
%%  \hspace{0.3cm}
%\subfloat[mistake1, boy S5]    
%    {\label{fig:domino-same-group1}\includegraphics[height=4cm]{domino-mistake1_S5.pdf}}
%%  \hspace{0.3cm}
%\subfloat[mistake1, boy S6]    
%    {\label{fig:domino-same-group2}\includegraphics[height=4cm]{domino-mistake1_S6.pdf}}    
%    
%  \caption[Individual Differences in Interacting with the Robot]{\small \textbf{Individual differences in interacting with the robot}. The top row with figures a) and b) shows the group \texttt{disobey3} that consisted of two boys. We consider this group as not aligned in their interaction with the robot. While the boy S16 in figure b) talks a lot the robot and also touches it frequently and uses gestures during the first runs, the other boy S15 in figure a) does not do so at all. The bottom row with figures c) and d) shows the group \texttt{mistake1} that also consisted of two boys. We consider this group as fairly aligned in their interaction with the robot. Both children tend to touch the robot and look at the experimenter.}
%  \label{fig:domino-individual-differences}
%\end{figure}

@@

%\begin{figure}[!h]
%  \centering
%	\subfloat[]    
%    {\label{fig:domino-imagine}\includegraphics[width=4.75cm]{domino-imagine.pdf}}
%%    \hspace{0.2cm}
%	\subfloat[]    
%    {\label{fig:domino-robot}\includegraphics[width=4.75cm]{domino-robot.pdf}}
%%	\hspace{0.2cm}
%	\subfloat[]	
%	{\label{fig:domino-ranger-how}\includegraphics[width=4.75cm]{domino-ranger-how.pdf}}
%  \caption[Expectations and Robot-likeness or Ranger]{\small \textbf{Expectations of robots in general and robot-likeness of Ranger.} When children had to justify why they thought Ranger is a robot (c), multiple answers were possible, we received 21 answers from 12 children.} 
%  \label{fig:domino-expectations}
%\end{figure}

@@

%\begin{figure}[!h]
%\centering
%  \includegraphics[height=6cm]{domino-why-misbehavior.pdf}   
%\caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible to the question why the robot did not come over, and we received 37 answers. This question shows that children did not necessarily interpret the misbehavior in the way we had assumed.}
%  \label{fig:domino-why-misbehavior}
%\end{figure}

@@

%\begin{figure}[!h]
%\centering
%  \subfloat[]
%  {\label{fig:domino-hear}
%  \includegraphics[height=5.5cm]{domino-hear.pdf}}
%  \subfloat[]
%  {\label{fig:domino-see}
%  \includegraphics[height=5.5cm]{domino-see.pdf}}   
%\caption[Attribution of Cognitive Skills to Ranger]{\small \textbf{Attribution of cognitive skills to Ranger.} These two questions were asked both in the first interview, after children had interacted with the correctly behaving robot, and in the second interview, after children had interacted with the unexpectedly behaving robot (three conditions). A comparison of the answers (first-second) can reveal to what extent the respective misbehavior of the robot impacted children's attribution of cognitive abilities. (Note that there were 10 participants in the disobey condition and each 8 participants in the mistake and lost condition. Consequently, here and in the following visualizations, we need to be careful as the bars are based on counting answers.) The three bars on the right side of each diagram are a split-up of the \textit{``all''} bar of the second time children were asked.}
%  \label{fig:domino-cognition}
%\end{figure}

@@

%\begin{figure}[h]
%\centering
%  \subfloat[]
%  {\label{fig:domino-obey}
%  \includegraphics[height=5.8cm]{domino-obey.pdf}}
%  \subfloat[]
%  {\label{fig:domino-silly}
%  \includegraphics[height=5.8cm]{domino-silly.pdf}}   
%\caption[Attribution of Intention to Ranger]{\small \textbf{Attribution of intention to Ranger.} Similar as before, children were asked these questions twice. Concerning question (a), there are no remarkable differences in children's responses given in the \textit{first} and \textit{second} interview. Children tend to think Ranger does always obey to them, even after it misbehaved (\textit{second} part). There is however a small difference in the responses visualized in graph (b). After the robot misbehaved, 8 children think the robot could do something silly whereas first, only 3 children answered like this.}
%  \label{fig:domino-intention}
%\end{figure}

@@

%\begin{figure}[!h]
%\centering
% \subfloat[]
%  {\label{fig:domino-feelings}
%  \includegraphics[height=5cm]{domino-feelings.pdf}}
% \subfloat[]
%  {\label{fig:domino-friend}
%  \includegraphics[height=5cm]{domino-friend.pdf}}
%\caption[Attribution of Emotional State and Perceived Companionship]{\small \textbf{Attributions of emotional state and perceived companionship}.}
%  \label{fig:domino-feelings-companion}
%\end{figure}

@@

%\begin{figure}[!h] \centering \subfloat[] {\label{fig:domino-leave}
%\includegraphics[height=5cm]{domino-leave.pdf}} \subfloat[]
%{\label{fig:domino-leave-why}
%\includegraphics[height=5cm]{domino-leave-why.pdf}} \caption[Attribution of
%Moral Standing]{\small \textbf{Attributions of moral standing}. We asked
%children whether it was alright to leave Ranger alone at home if they go on a
%2-week vacation (a). Multiple answers (open-ended) were allowed when asked to
%justify their answer (b).} \label{fig:domino-leave-alone} \end{figure}

@@

%\begin{figure}[!h]
%\centering
% \subfloat[]
%  {\label{fig:domino-like}
%  \includegraphics[height=5cm]{domino-like.pdf}}
% \subfloat[]
%  {\label{fig:domino-leave-athome}
%  \includegraphics[height=5cm]{domino-athome.pdf}}
%\caption[Acceptance of Ranger]{\small \textbf{Acceptance of Ranger}.}
%  \label{fig:domino-acceptance}
%\end{figure}

>>>>

\begin{figure}[!h]
  \centering
\subfloat[total number (count, \%)]    
    {\label{fig:domino-action-count}\includegraphics[height=5cm]{domino_actions-pie.pdf}}
%  \hspace{0.3cm}
\subfloat[annotation duration, (\%)]    
    {\label{fig:domino-action-time}\includegraphics[height=5cm]{domino_duration-pie.pdf}}

  \caption[Total Number and Duration of Children's Actions with Ranger]{\small \textbf{Children's actions with Ranger.} (a) shows the total number of the counted actions that were annotated in the videos, (b) shows the total annotation duration percentage of these actions (the total duration of all coded actions are considered as 100\%, not the duration of the scenario).}
  \label{fig:domino-actions-pie}
\end{figure}

@@

\begin{figure}[!b] 
\centering 
\includegraphics[width=0.99\columnwidth]{domino-time-all.pdf} 
\caption[Number and Type of Actions for Each Run]{\small \textbf{Number and type of actions for each run} (average for one child per minute). Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9). The first 7 runs correspond to the \textit{expected phase}, the second 7 runs correspond to the \textit{unexpected phase}. Especially during run 2.3, the first time when the robot showed an unexpected behavior, children tended to \textit{look} more at the experimenter. During the unexpected phase, also \textit{talk} and \textit{gesture} seem to be increased. The specific values comparing the expected and unexpected phases overall are presented in Table \ref{tab:domino-conditions}, page~\pageref{tab:domino-conditions}.}
\label{fig:domino-time-all} 
\end{figure}

@@

\begin{figure}[!h] 
\centering 
\includegraphics[width=0.9\columnwidth]{domino-actions-perrun.pdf} 
\caption[Total Number of Actions for Each Run per Condition]{\small \textbf{Total number of actions for each run per condition} (average for one child per minute). Generally, the number of actions does not decrease over time (from run 1.1 to run 2.9). Especially during run 2.3, the first time when the robot showed an unexpected behavior, children interact more with the robot, as well as during run 2.7 when the robot misbehaved again after two correct runs. Another increase of actions is during the very last run.}
\label{fig:domino-time-condition-one} 
\end{figure}

@@

\begin{figure}[!t] 
\centering 
\includegraphics[width=0.5\columnwidth]{domino-engagement-condition.pdf} 
\caption[Engagement Actions in Expected and Unexpected Phase]{\small \textbf{Average number of engagement actions in expected and unexpected phase.} In all three behavior conditions, children engage more in the unexpected phase. In general, the \textit{lost} and \textit{mistake} misbehavior are more engaging than the \textit{disobeying} behavior.} 
\label{fig:domino-engagement-condition} 
\end{figure}

@@

\begin{figure}[!h] 
\centering 
\includegraphics[width=0.99\columnwidth]{domino-time-active.pdf} 
\caption[Engagement Actions for Each Run]{\small \textbf{Engagement actions for each run} (without explore). Average for one child per minute.}
\label{fig:domino-time-active} 
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \subfloat[disobey3, boy S15]    
    {\label{fig:domino-diff-group1}\includegraphics[height=4cm]{domino-disobey3_S15.pdf}}
    %  \hspace{0.3cm}
    \subfloat[disobey3, boy S16]    
    {\label{fig:domino-diff-group2}\includegraphics[height=4cm]{domino-disobey3_S16.pdf}}\\
    %  \hspace{0.3cm}
    \subfloat[mistake1, boy S5]    
    {\label{fig:domino-same-group1}\includegraphics[height=4cm]{domino-mistake1_S5.pdf}}
    %  \hspace{0.3cm}
    \subfloat[mistake1, boy S6]    
    {\label{fig:domino-same-group2}\includegraphics[height=4cm]{domino-mistake1_S6.pdf}}

    \caption[Individual Differences in Interacting with the Robot]{\small
        \textbf{Individual differences in interacting with the robot}. The top row
        with figures a) and b) shows the group \texttt{disobey3} that consisted of two
        boys. We consider this group as not aligned in their interaction with the
        robot. While the boy S16 in figure b) talks a lot the robot and also touches
        it frequently and uses gestures during the first runs, the other boy S15 in
        figure a) does not do so at all. The bottom row with figures c) and d) shows
        the group \texttt{mistake1} that also consisted of two boys. We consider this
        group as fairly aligned in their interaction with the robot. Both children
        tend to touch the robot and look at the experimenter.}

    \label{fig:domino-individual-differences}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \subfloat[] {
        \label{fig:domino-imagine}
        \includegraphics[width=4.75cm]{domino-imagine.pdf}
    }
    %    \hspace{0.2cm}
    \subfloat[] {
        \label{fig:domino-robot}
        \includegraphics[width=4.75cm]{domino-robot.pdf}
    }
    %	\hspace{0.2cm}
    \subfloat[]	{
        \label{fig:domino-ranger-how}
        \includegraphics[width=4.75cm]{domino-ranger-how.pdf}
    }
    \caption[Expectations and Robot-likeness or Ranger]{\small
    \textbf{Expectations of robots in general and robot-likeness of Ranger.}
    When children had to justify why they thought Ranger is a robot (c), multiple
    answers were possible, we received 21 answers from 12 children.}

    \label{fig:domino-expectations}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[height=6cm]{domino-why-misbehavior.pdf}   
    \caption[Why Did the Robot Misbehave?]{\small Multiple answers were possible
    to the question why the robot did not come over, and we received 37 answers.
    This question shows that children did not necessarily interpret the misbehavior
    in the way we had assumed.}

    \label{fig:domino-why-misbehavior}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \subfloat[]{
        \label{fig:domino-hear}
        \includegraphics[height=5.5cm]{domino-hear.pdf}
    }
    \subfloat[] {
        \label{fig:domino-see}
        \includegraphics[height=5.5cm]{domino-see.pdf}
    }
    \caption[Attribution of Cognitive Skills to Ranger]{\small
    \textbf{Attribution of cognitive skills to Ranger.} These two questions were
    asked both in the first interview, after children had interacted with the
    correctly behaving robot, and in the second interview, after children had
    interacted with the unexpectedly behaving robot (three conditions). A comparison
    of the answers (first-second) can reveal to what extent the respective
    misbehavior of the robot impacted children's attribution of cognitive abilities.
    (Note that there were 10 participants in the disobey condition and each 8
    participants in the mistake and lost condition. Consequently, here and in the
    following visualizations, we need to be careful as the bars are based on
    counting answers.) The three bars on the right side of each diagram are a
    split-up of the \textit{``all''} bar of the second time children were asked.}

    \label{fig:domino-cognition}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \subfloat[] {
        \label{fig:domino-obey}
        \includegraphics[height=5.8cm]{domino-obey.pdf}
    }
    \subfloat[] {
        \label{fig:domino-silly}
        \includegraphics[height=5.8cm]{domino-silly.pdf}
    }
    \caption[Attribution of Intention to Ranger]{\small \textbf{Attribution of
    intention to Ranger.} Similar as before, children were asked these questions
    twice. Concerning question (a), there are no remarkable differences in
    children's responses given in the \textit{first} and \textit{second} interview.
    Children tend to think Ranger does always obey to them, even after it misbehaved
    (\textit{second} part). There is however a small difference in the responses
    visualized in graph (b). After the robot misbehaved, 8 children think the robot
    could do something silly whereas first, only 3 children answered like this.}

    \label{fig:domino-intention}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \subfloat[]
    {   \label{fig:domino-feelings}
        \includegraphics[height=5cm]{domino-feelings.pdf}}
    \subfloat[]
    {   \label{fig:domino-friend}
        \includegraphics[height=5cm]{domino-friend.pdf}}
    \caption[Attribution of Emotional State and Perceived Companionship]{\small
    \textbf{Attributions of emotional state and perceived companionship}.}

    \label{fig:domino-feelings-companion}
\end{figure}

@@

\begin{figure}[!h]
    \centering 
    \subfloat[] {
        \label{fig:domino-leave}
        \includegraphics[height=5cm]{domino-leave.pdf}
    } 
    \subfloat[] {
        \label{fig:domino-leave-why}
        \includegraphics[height=5cm]{domino-leave-why.pdf}
    } 
    \caption[Attribution of Moral Standing]{\small \textbf{Attributions of moral
        standing}. We asked children whether it was alright to leave Ranger
        alone at home if they go on a 2-week vacation (a). Multiple answers
        (open-ended) were allowed when asked to justify their answer (b).}

    \label{fig:domino-leave-alone} 
\end{figure}

@@

\begin{figure}[!h]
\centering
 \subfloat[]
  {\label{fig:domino-like}
  \includegraphics[height=5cm]{domino-like.pdf}}
 \subfloat[]
  {\label{fig:domino-leave-athome}
  \includegraphics[height=5cm]{domino-athome.pdf}}
\caption[Acceptance of Ranger]{\small \textbf{Acceptance of Ranger}.}
  \label{fig:domino-acceptance}
\end{figure}
